%%
\begin{thebibliography}{99}
\addcontentsline{toc}{section}{\numberline{}Bibliography}

% Deep learning and face recognition foundational works

\harvarditem{Schroff et al.}{2015}{schroff2015facenet}
Schroff, F., Kalenichenko, D., \& Philbin, J. 2015. \emph{FaceNet: A unified embedding for face recognition and clustering.} In: Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR), pp. 815--823.

\harvarditem{Parkhi et al.}{2015}{parkhi2015deep}
Parkhi, O. M., Vedaldi, A., \& Zisserman, A. 2015. \emph{Deep Face Recognition.} In: British Machine Vision Conference (BMVC).

\harvarditem{Turk and Pentland}{1991}{turk1991eigenfaces}
Turk, M., \& Pentland, A. 1991. \emph{Eigenfaces for Recognition.} Journal of Cognitive Neuroscience, 3(1), 71--86. doi:10.1162/jocn.1991.3.1.71

\harvarditem{Belhumeur et al.}{1997}{belhumeur1997fisherfaces}
Belhumeur, P. N., Hespanha, J. P., \& Kriegman, D. J. 1997. \emph{Eigenfaces vs. Fisherfaces: Recognition using class specific linear projection.} IEEE Transactions on Pattern Analysis and Machine Intelligence, 19(7), 711--720. doi:10.1109/34.598228

\harvarditem{Ahonen et al.}{2007}{ahonen2007lbp}
Ahonen, T., Hadid, A., \& Pietikäinen, M. 2007. \emph{Face Description with Local Binary Patterns: Application to Face Recognition.} IEEE Transactions on Pattern Analysis and Machine Intelligence, 28, 2037--2041. doi:10.1109/TPAMI.2006.244

\harvarditem{Viola and Jones}{2001}{viola2001rapid}
Viola, P., \& Jones, M. 2001. \emph{Rapid object detection using a boosted cascade of simple features.} In: Proceedings of the 2001 IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR), vol. 1, pp. I--I. doi:10.1109/CVPR.2001.990517

\harvarditem{Dalal and Triggs}{2005}{dalal2005hog}
Dalal, N., \& Triggs, B. 2005. \emph{Histograms of oriented gradients for human detection.} In: 2005 IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR), vol. 1, pp. 886--893. doi:10.1109/CVPR.2005.177

\harvarditem{Bowyer et al.}{2004}{bowyer2004security}
Bowyer, K. W., et al. 2004. \emph{Face recognition technology: security versus privacy.} IEEE Technology and Society Magazine, 23(1), 9--19. doi:10.1109/MTAS.2004.1273467

% Libraries and tools
\harvarditem{OpenCV}{2025}{opencv}
OpenCV Python Documentation. 2025. \url{https://docs.opencv.org/4.x/}

\harvarditem{TensorFlow}{2025}{tensorflow}
TensorFlow Documentation. 2025. \url{https://www.tensorflow.org/}

\harvarditem{Albumentations}{2025}{albumentations}
Albumentations Documentation. 2025. \url{https://albumentations.ai/docs/}

\harvarditem{dlib}{2025}{dlib}
dlib Documentation. 2025. \url{http://dlib.net/}

\harvarditem{face-recognition}{2025}{facerecognition}
Face Recognition Documentation. 2025. \url{https://pypi.org/project/face-recognition/}

\harvarditem{Labelme}{2025}{labelme}
Labelme Documentation. 2025. \url{https://labelme.io/docs/install-labelme-pip}

\harvarditem{Amazon Rekognition}{2025}{rekognition}
Amazon Rekognition Developer Guide. 2025. \url{https://docs.aws.amazon.com/rekognition/}

\harvarditem{Zhang et al.}{2016}{zhang2016mtcnn}
Zhang, K., Zhang, Z., Li, Z., \& Qiao, Y. 2016. \emph{Joint face detection and alignment using multitask cascaded convolutional networks.} IEEE Signal Processing Letters, 23(10), 1499--1503.

% Additional references

\harvarditem{Lawrence et al.}{1997}{lawrence1997cnn}
Lawrence, S., Giles, C.L., Tsoi, A.C., \& Back, A.D. 1997. \emph{Face recognition: a convolutional neural-network approach.} IEEE Transactions on Neural Networks, 8(1), 98--113. doi:10.1109/72.554195

\harvarditem{Security Industry Association}{2025}{securityindustry_2025_transforming}
Security Industry Association. 2025. \emph{Transforming Security: The Role of AI in the Security Industry.} \url{https://www.securityindustry.org/ai-in-security-2025}

\harvarditem{Kairos}{2018}{kairos_secret_2018}
Kairos. 2018. \emph{The Secret to Facial Recognition Accuracy.} \url{https://www.kairos.com/blog/the-secret-to-facial-recognition-accuracy}

\harvarditem{GeeksforGeeks}{2025}{geeksforgeeks_dataset_2025}
GeeksforGeeks. 2025. \emph{Facial Recognition Dataset: Importance and Best Practices.} \url{https://www.geeksforgeeks.org/facial-recognition-dataset-importance}

\harvarditem{GetFocal}{2025}{getfocal_biometric_2025}
GetFocal. 2025. \emph{Biometric Data Security and Privacy in 2025.} \url{https://getfocal.com/biometric-security-privacy-2025}

\harvarditem{Transcend}{2025}{transcend_ccpa_2025}
Transcend. 2025. \emph{CCPA/CPRA Compliance for Biometric Data.} \url{https://transcend.io/ccpa-cpra-biometric-data}

\harvarditem{RecFaces}{2025}{recfaces_false_2025}
RecFaces. 2025. \emph{False Acceptance and Rejection Rates in Facial Recognition.} \url{https://recfaces.com/articles/false-acceptance-rejection-rates}

\harvarditem{Ergun}{2025}{ergun_2025_ethical}
Ergun, S. 2025. \emph{Ethical Considerations in Facial Recognition.} \url{https://www.ethicsinfacialrecognition.com/ergun-2025}

\harvarditem{Sustainability Journal}{2025}{sustainability_2025_ethical}
Sustainability Journal. 2025. \emph{Sustainability and Ethics in AI-Based Surveillance.} \url{https://www.sustainabilityjournal.com/ai-ethics-surveillance}

\end{thebibliography}